(Tentative) Calculating Green Function

### 2016-09-05 Green function/green-f.tex
Updated Green function.

In that formalism, the currents following through the leads have the following
expression:
\begin{align}
    I_p = \frac{-e}{h} \sum_q \int T_{qp}(E)\left( f_p(E)-f_q(E) \right)\diff E
\end{align}
where $T_{pq}$ is the transmission coefficients for electrons to go from
lead $q$ to lead $p$. This formula can be simplified/linearized into:
\begin{align}
    I_p = \frac{e^2}{h}\sum_q T_{pq}(E_F)(V_p-V_q)
\end{align}
An obvious advantage of Landauer-Büttiker formalism is that it makes the
dependence of $I_p$ on experimental setup explicit in the formula.

@@

\section{Chapter 3 Tight-binding model}
\label{sec:Chapter_3_Tight-binding_model}

Here in this chapter the author presents the fundamental Hamiltonian of
the system under consideration.
\marginpar{
    Given the formula mentioned in previous chapter, the Hamiltonian
    presented here seemed extraneous. Maybe the author wants to examine
    the physics in more detail.
}

@@

\section{Anchor}

>>>>

In that formalism, the currents following through the leads have the following
expression:
\begin{align}
    \label{eq:ch1.Landauer-Buttiker_formula}
    I_p = \frac{-e}{h} \sum_q \int T_{qp}(E)\left( f_p(E)-f_q(E) \right)\diff E
\end{align}
where $T_{pq}$ is the transmission coefficients for electrons to go from
lead $q$ to lead $p$. This formula can be simplified/linearized into:
\begin{align}
    I_p = \frac{e^2}{h}\sum_q T_{pq}(E_F)(V_p-V_q)
\end{align}
An obvious advantage of Landauer-Büttiker formalism is that it makes the
dependence of $I_p$ on experimental setup explicit in the formula.

@@

\section{Chapter 3 - Tight-binding model}
\label{sec:Chapter_3_Tight-binding_model}

Here in this chapter the author presents the fundamental Hamiltonian of
the system under consideration.
\marginpar{
    Given the formula mentioned in previous chapter, the Hamiltonian
    presented here seemed seemingly extraneous. Read the introduction
    here in chapter 4 to understand the underlying logic.
}

@@

\section{Chapter 4 - Green’s function formalism}
\label{sec:Chapter_4-Greens_function_formalism}

In this section we finally circled back to the Landauer-Büttiker
formalism. Here a breif summary of chapter 3 and 4 is opportune.
The purpose of chapter 3 and 4 as a whole, is to calculate the 
transmission coefficient $T_{qp}$ in equation
\ref{eq:ch1.Landauer-Buttiker_formula}. Here, chapter 3 establish the
Hamiltonian, and chapter 4 uses the Green function to calculate
transmission coefficient out of the Hamiltonian.

    \subsection{4.1 Green’s functions: The basics}
    \label{sec:4.1_Greens_functions_The_basics}

    The author takes the definition of Green's function as inverse
    of Hamiltonian, more specifically:
    \begin{align}
        [E-\hat{H}]\hat{G}(E) = 1
    \end{align}
    or, in the position-spin representation:
    \begin{align}
        [E-H(\vec{x})]G(\vec{x},\vec{x'},E)=\delta(\vec{x}-\vec{x'})
    \end{align}
    where $\vec{x}=(\vec{r},\sigma)$, containing in addition to the
    usual spatial part, the spin part.

    The physical meaning is also explained, although I learnt this
    better in A. Zee's QFT in a Nutshell. However, he notes that
    to disguish between the source and sink, i.e. to tell whether
    the Green's function calculated represents a wavefunction
    resulted from a unit excitation (the sink), or a source for such
    an excitation, we should incorporate boundary conditions. This is
    done by adding "an infinitesimal imaginary variable into the energy",
    "leading to the following definitions":
    \begin{align}
        G^{\pm}(\vec{x},\vec{x'},E)\equiv \lim_{\eta\to 0^{+}}
            G(\vec{x},\vec{x'},E\pm i\eta)
    \end{align}
    and $G^{\pm}$ satisfies:
    \begin{align}
        [E\pm i\eta - H(\vec{x})] G^{\pm}(\vec{x},\vec{x'},E)=
            \sigma(\vec{x}-\vec{x'})
    \end{align}
    The functions $G^+$ and $G^-$ are called respectively the
    \textbf{retarded and advanced Green's function}. The author
    mentions that, "when Fourier transforming the functions $G^\pm$ to
    the time domain using a closed contour integration in the complex 
    plane, they would correspond to causal and anticausal solutions".

    Though seemingly extraneous, the operator definition for above
    Green functions is also mentioned:
    \begin{align}
        \hat{G}^{\pm}(E)\equiv \lim_{\eta\to 0^+}
            \frac{1}{E\pm i\eta-\hat{H}}
    \end{align}
    \subsection{4.2 Transmission coefficients and the Green’s function}
    \label{sec:4.2_Transmission_coefficients_and_the_Greens_function}

    Here it is mentioned than the transmission coefficient is related
    Green's funciton in the following way:
    \begin{align}
        T_{pq} = \text{Tr}\left[\Gamma_p G_{pq}\Gamma_q G^{\dagger}_{pq}
                \right]
    \end{align}
    Here $G_{pq}$ is, to borrow the language of matrix mechanics,
    a submatrix of the Green's function. $\Gamma_p$ is a abbreviation
    for the following counting:
    \marginpar{I am not sure about this peculiar thing.}
    \begin{align}
        \label{eq:}
        \Gamma_p \equiv i(\sum_p-\sum^\dagger_p)
    \end{align}
    Here $\sum_p$ is named "self-energy of the lead", something I
    don't quite understand.
\section{Anchor}
